\textit{F1000Research} Associations between chlorophyll \emph{a} and various microcystin-LR health advisory Concentrations

### 2016-01-17 manuscript/manuscript.Rmd
f1000 foramt almost working.  Need to figure out tables and figures

---
title: Associations between chlorophyll *a* and various microcystin-LR health advisory
  Concentrations
author:
- affilnum: 1
  email: hollister.jeff@epa.gov
  name: Jeffrey W. Hollister
- affilnum: 1
  name: Betty J. Kreakie
affiliation:
- affil: US Environmental Protection Agency, Office of Research and Development, National
    Health and Environmental Effects Research Laboratory, Atlantic Ecology Division,
    27 Tarzwell Drive  Narragansett, RI, 02882, USA
  affilnum: 1
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    template: components/f1000research.latex
  html_document: null
capsize: normalsize
csl: components/plos.csl
documentclass: article
fontsize: 11pt
linenumbers: yes
bibliography: components/manuscript.bib
spacing: doublespacing
abstract: no
---

@@

\singlespace

@@

<!-- Abstract is being wrapped in latex here so that all analysis can be run in the chunk above and the results reproducibly referenced in the abstract. -->
Cyanobacteria harmful algal blooms (cHABs) are associated with a wide range of adverse health effects that stem mostly from the presence of cyanotoxins.  To help protect against these impacts, several health advisory levels have been set for some toxins.  In particular, one of the more common toxins, microcystin, has several advisory levels set for drinking water and recreational use.  However, compared to other water quality measures, field measurements of microcystin are not commonly available due to cost and advanced understanding required to interpret results.  Addressing these issues will take time and resources.  Thus, there is utility in finding indicators of microcystin that are already widely available, can be estimated quickly and *in situ*, and used as a first defense against high levels of microcystin.  Chlorophyll *a* is commonly measured, can be estimated *in situ*, and has been shown to be positively associated with microcystin.  In this paper, we use this association to provide estimates of chlorophyll *a* concentrations that are indicative of a higher probability of exceeding select health advisory concentrations for microcystin-LR.  Using the 2007 National Lakes Assessment and a conditional probability approach, we identify chlorophyll *a* concentrations that are more likely than not to be associated with an exceedance of a microcystin health advisory level.  We look at the recent US EPA health advisories for drinking water as well as the World Health Organization levels for drinking water and recreational use and identify a range of chlorophyll *a* thresholds.  A 50% chance of exceeding one of the specific advisory microcystin concentrations of 0.3, 1, 1.6, and 2 $\mu$g/L is associatied with chlorophyll *a* concentration thresholds of `r mc_chla[5,1]`, `r mc_chla[5,2]`, `r mc_chla[5,3]`, and `r mc_chla[5,4]`, respectively.  When managing for these various microcystin levels, exceeding these reported chlorophyll *a* concentrations should be a trigger for further testing and possible management action.

\vspace{3mm}\hrule
\doublespace

#Introduction

@@

```{r microcystin_levels,echo=FALSE,results='asis', tab.cap="Various suggested microcystin-LR health advisory concentrations. \\label{tab:microcystin_levels}"}
source_of_stnd <- c("WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "USEPA",
                    "USEPA")
type_of_stnd <- c("Recreational: Low Prob. of Effect",
                  "Recreational: Moderate Prob. of Effect",
                  "Recreational: High Prob. of Effect",
                  "Recreational: Very High Prob. of Effect",
                  "Drinking Water",
                  "Child Drinking Water Advisory",
                  "Adult Drinking Water Advisory")
concentration <- c("2-4 $\\mu$g/L",
                   "10-20 $\\mu$g/L",
                   "20-2000 $\\mu$g/L",
                   ">2000 $\\mu$g/L",
                   "1 $\\mu$g/L",
                   "0.3 $\\mu$g/L",
                   "1.6 $\\mu$g/L")
#note <- c("Low probability of adverse health effects",
#          "Moderate probability of adverse health effects",
#          "High probability of adverse health effects, These higher #concentrations typically only seen in visible scums/algal mats",
#          "Very high probability of adverse health effects",
#          "",
#          "Children younger than school age",
#          "Individuals School age and older")
mc_conc_table <- data.frame(source_of_stnd, type_of_stnd, concentration) %>%
  arrange(type_of_stnd)
names(mc_conc_table)<-c("Source","Type","Concentration")
#pandoc.table(mc_conc_table,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
knitr::kable(mc_conc_table)
```

@@

```{r mc_chla_table, results='asis', echo=FALSE, tab.cap="Chlorophyll \\textit{a} concentrations that are associated with a 50% probability of exceeding a microcystin-LR health advisory concentration. \\label{tab:mc_chla_table}"}
mc_chla_tbl <- data.frame(seq(0.1,0.9,0.1),mc_chla)
names(mc_chla_tbl)<-c("Cond. Probability","USEPA Child", "WHO Drink", 
                      "USEPA Adult", "WHO Recreational")
#pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
knitr::kable(mc_chla_tbl)
```

@@

```{r child_conmat_table, results='asis', echo=FALSE, tab.cap="Confusion matrix comparing chlorophyll \\textit{a} predicted exceedences (rows) versus real exceedances (columns) for the USEPA childrens drinking water advisory. \\label{tab:child_conmat_table}"}
knitr::kable(child_conmat)
```

@@

```{r who_drink_conmat_table, results='asis', echo=FALSE, tab.cap="Confusion matrix comparing chlorophyll \\textit{a} predicted exceedences (rows) versus real exceedances (columns) for the WHO drinking water advisory. \\label{tab:who_drink_conmat_table}"}
knitr::kable(who_drink_conmat)
```

@@

```{r adult_conmat_table, results='asis', echo=FALSE, tab.cap="Confusion matrix comparing chlorophyll \\textit{a} predicted exceedences (rows) versus real exceedances (columns) for the USEPA adult drinking water advisory. \\label{tab:adult_conmat_table}"}
knitr::kable(adult_conmat)
```

@@

```{r who_rec_conmat_table, results='asis', echo=FALSE, tab.cap="Confusion matrix comparing chlorophyll \\textit{a} predicted exceedences (rows) versus real exceedances (columns) for the WHO recreational water advisory. \\label{tab:who_rec_conmat_table}"}
knitr::kable(who_rec_conmat)
```

>>>>

---
title: Associations between chlorophyll *a* and various microcystin-LR health advisory
  Concentrations
author:
- affilnum: 1
  email: hollister.jeff@epa.gov
  name: Jeffrey W. Hollister
- affilnum: 1
  name: Betty J. Kreakie
affiliation:
- affil: US Environmental Protection Agency, Office of Research and Development, National
    Health and Environmental Effects Research Laboratory, Atlantic Ecology Division,
    27 Tarzwell Drive  Narragansett, RI, 02882, USA
  affilnum: 1
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    template: components/f1000research.latex
  html_document: null
capsize: normalsize
csl: components/plos.csl
documentclass: article
fontsize: 11pt
linenumbers: yes
bibliography: components/manuscript.bib
spacing: doublespacing
abstract: "Cyanobacteria harmful algal blooms (cHABs) are associated with a wide range of adverse health effects that stem mostly from the presence of cyanotoxins. To help protect against these impacts, several health advisory levels have been set for some toxins. In particular, one of the more common toxins, microcystin, has several advisory levels set for drinking water and recreational use. However, compared to other water quality measures, field measurements of microcystin are not commonly available due to cost and advanced understanding required to interpret results. Addressing these issues will take time and resources. Thus, there is utility in finding indicators of microcystin that are already widely available, can be estimated quickly and in situ, and used as a first defense against high levels of microcystin. Chlorophyll *a* is commonly measured, can be estimated *in situ*, and has been shown to be positively associated with microcystin. In this paper, we use this association to provide estimates of chlorophyll a concentrations that are indicative of a higher probability of exceeding select health advisory concentrations for microcystin-LR. Using the 2007 National Lakes Assessment and a conditional probability approach, we identify chlorophyll *a* concentrations that are more likely than not to be associated with an exceedance of a microcystin health advisory level. We look at the recent US EPA health advisories for drinking water as well as the World Health Organization levels for drinking water and recreational use and identify a range of chlorophyll *a* thresholds. A 50% chance of exceeding one of the specific advisory microcystin concentrations of 0.3, 1, 1.6, and 2 g/L is associatied with chlorophyll *a* concentration thresholds of 24.64, 65.6, 89.71, and 94.93, respectively. When managing for these various microcystin levels, exceeding these reported chlorophyll *a* concentrations should be a trigger for further testing and possible management action."
---

@@

<!--
\singlespace

@@

<!-- Abstract is being wrapped in latex here so that all analysis can be run in the chunk above and the results reproducibly referenced in the abstract. 
Cyanobacteria harmful algal blooms (cHABs) are associated with a wide range of adverse health effects that stem mostly from the presence of cyanotoxins.  To help protect against these impacts, several health advisory levels have been set for some toxins.  In particular, one of the more common toxins, microcystin, has several advisory levels set for drinking water and recreational use.  However, compared to other water quality measures, field measurements of microcystin are not commonly available due to cost and advanced understanding required to interpret results.  Addressing these issues will take time and resources.  Thus, there is utility in finding indicators of microcystin that are already widely available, can be estimated quickly and *in situ*, and used as a first defense against high levels of microcystin.  Chlorophyll *a* is commonly measured, can be estimated *in situ*, and has been shown to be positively associated with microcystin.  In this paper, we use this association to provide estimates of chlorophyll *a* concentrations that are indicative of a higher probability of exceeding select health advisory concentrations for microcystin-LR.  Using the 2007 National Lakes Assessment and a conditional probability approach, we identify chlorophyll *a* concentrations that are more likely than not to be associated with an exceedance of a microcystin health advisory level.  We look at the recent US EPA health advisories for drinking water as well as the World Health Organization levels for drinking water and recreational use and identify a range of chlorophyll *a* thresholds.  A 50% chance of exceeding one of the specific advisory microcystin concentrations of 0.3, 1, 1.6, and 2 $\mu$g/L is associatied with chlorophyll *a* concentration thresholds of `r mc_chla[5,1]`, `r mc_chla[5,2]`, `r mc_chla[5,3]`, and `r mc_chla[5,4]`, respectively.  When managing for these various microcystin levels, exceeding these reported chlorophyll *a* concentrations should be a trigger for further testing and possible management action.

\vspace{3mm}\hrule
\doublespace
-->
#Introduction

@@

```{r microcystin_levels,echo=FALSE,results='asis', tab.cap="Various suggested microcystin-LR health advisory concentrations. \\label{tab:microcystin_levels}"}
source_of_stnd <- c("WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "USEPA",
                    "USEPA")
type_of_stnd <- c("Recreational: Low Prob. of Effect",
                  "Recreational: Moderate Prob. of Effect",
                  "Recreational: High Prob. of Effect",
                  "Recreational: Very High Prob. of Effect",
                  "Drinking Water",
                  "Child Drinking Water Advisory",
                  "Adult Drinking Water Advisory")
concentration <- c("2-4 $\\mu$g/L",
                   "10-20 $\\mu$g/L",
                   "20-2000 $\\mu$g/L",
                   ">2000 $\\mu$g/L",
                   "1 $\\mu$g/L",
                   "0.3 $\\mu$g/L",
                   "1.6 $\\mu$g/L")
#note <- c("Low probability of adverse health effects",
#          "Moderate probability of adverse health effects",
#          "High probability of adverse health effects, These higher #concentrations typically only seen in visible scums/algal mats",
#          "Very high probability of adverse health effects",
#          "",
#          "Children younger than school age",
#          "Individuals School age and older")
mc_conc_table <- data.frame(source_of_stnd, type_of_stnd, concentration) %>%
  arrange(type_of_stnd)
names(mc_conc_table)<-c("Source","Type","Concentration")
#pandoc.table(mc_conc_table,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
knitr::kable(mc_conc_table,format="latex")
```

@@

```{r mc_chla_table, results='asis', echo=FALSE, tab.cap="Chlorophyll \\textit{a} concentrations that are associated with a 50% probability of exceeding a microcystin-LR health advisory concentration. \\label{tab:mc_chla_table}"}
mc_chla_tbl <- data.frame(seq(0.1,0.9,0.1),mc_chla)
names(mc_chla_tbl)<-c("Cond. Probability","USEPA Child", "WHO Drink", 
                      "USEPA Adult", "WHO Recreational")
#pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
knitr::kable(mc_chla_tbl,format="latex")
```

@@

```{r child_conmat_table, results='asis', echo=FALSE, tab.cap="Confusion matrix comparing chlorophyll \\textit{a} predicted exceedences (rows) versus real exceedances (columns) for the USEPA childrens drinking water advisory. \\label{tab:child_conmat_table}"}
knitr::kable(child_conmat,format="latex")
```

@@

```{r who_drink_conmat_table, results='asis', echo=FALSE, tab.cap="Confusion matrix comparing chlorophyll \\textit{a} predicted exceedences (rows) versus real exceedances (columns) for the WHO drinking water advisory. \\label{tab:who_drink_conmat_table}"}
knitr::kable(who_drink_conmat,format="latex")
```

@@

```{r adult_conmat_table, results='asis', echo=FALSE, tab.cap="Confusion matrix comparing chlorophyll \\textit{a} predicted exceedences (rows) versus real exceedances (columns) for the USEPA adult drinking water advisory. \\label{tab:adult_conmat_table}"}
knitr::kable(adult_conmat,format="latex")
```

@@

```{r who_rec_conmat_table, results='asis', echo=FALSE, tab.cap="Confusion matrix comparing chlorophyll \\textit{a} predicted exceedences (rows) versus real exceedances (columns) for the WHO recreational water advisory. \\label{tab:who_rec_conmat_table}"}
knitr::kable(who_rec_conmat,format="latex")
```

### 2016-01-17 manuscript/manuscript.tex
f1000 foramt almost working.  Need to figure out tables and figures

\documentclass[10pt,a4paper,twocolumn]{article}
\usepackage{f1000_styles}
\bibliography{components/manuscript}

@@

@@

\singlespace

\vspace{2mm}

\hrule

Cyanobacteria harmful algal blooms (cHABs) are associated with a wide
range of adverse health effects that stem mostly from the presence of
cyanotoxins. To help protect against these impacts, several health
advisory levels have been set for some toxins. In particular, one of the
more common toxins, microcystin, has several advisory levels set for
drinking water and recreational use. However, compared to other water
quality measures, field measurements of microcystin are not commonly
available due to cost and advanced understanding required to interpret
results. Addressing these issues will take time and resources. Thus,
there is utility in finding indicators of microcystin that are already
widely available, can be estimated quickly and \emph{in situ}, and used
as a first defense against high levels of microcystin. Chlorophyll
\emph{a} is commonly measured, can be estimated \emph{in situ}, and has
been shown to be positively associated with microcystin. In this paper,
we use this association to provide estimates of chlorophyll \emph{a}
concentrations that are indicative of a higher probability of exceeding
select health advisory concentrations for microcystin-LR. Using the 2007
National Lakes Assessment and a conditional probability approach, we
identify chlorophyll \emph{a} concentrations that are more likely than
not to be associated with an exceedance of a microcystin health advisory
level. We look at the recent US EPA health advisories for drinking water
as well as the World Health Organization levels for drinking water and
recreational use and identify a range of chlorophyll \emph{a}
thresholds. A 50\% chance of exceeding one of the specific advisory
microcystin concentrations of 0.3, 1, 1.6, and 2 \(\mu\)g/L is
associatied with chlorophyll \emph{a} concentration thresholds of 21.92,
77.2, 84.96, and 105.84, respectively. When managing for these various
microcystin levels, exceeding these reported chlorophyll \emph{a}
concentrations should be a trigger for further testing and possible
management action.

\vspace{3mm}

\hrule

\doublespace

@@

\begin{longtable}[c]{@{}lll@{}}
\caption{Various suggested microcystin-LR health advisory
concentrations. \label{tab:microcystin_levels}}\tabularnewline
\toprule
Source & Type & Concentration\tabularnewline
\midrule
\endfirsthead
\toprule
Source & Type & Concentration\tabularnewline
\midrule
\endhead
USEPA & Adult Drinking Water Advisory & 1.6 \(\mu\)g/L\tabularnewline
USEPA & Child Drinking Water Advisory & 0.3 \(\mu\)g/L\tabularnewline
WHO & Drinking Water & 1 \(\mu\)g/L\tabularnewline
WHO & Recreational: High Prob. of Effect & 20-2000
\(\mu\)g/L\tabularnewline
WHO & Recreational: Low Prob. of Effect & 2-4 \(\mu\)g/L\tabularnewline
WHO & Recreational: Moderate Prob. of Effect & 10-20
\(\mu\)g/L\tabularnewline
WHO & Recreational: Very High Prob. of Effect & \textgreater{}2000
\(\mu\)g/L\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[c]{@{}rrrrr@{}}
\caption{Chlorophyll \textit{a} concentrations that are associated with
a 50\% probability of exceeding a microcystin-LR health advisory
concentration. \label{tab:mc_chla_table}}\tabularnewline
\toprule
Cond. Probability & USEPA Child & WHO Drink & USEPA Adult & WHO
Recreational\tabularnewline
\midrule
\endfirsthead
\toprule
Cond. Probability & USEPA Child & WHO Drink & USEPA Adult & WHO
Recreational\tabularnewline
\midrule
\endhead
0.1 & 0.07 & 0.07 & 0.07 & 1.17\tabularnewline
0.2 & 0.07 & 4.48 & 10.67 & 18.24\tabularnewline
0.3 & 2.78 & 17.49 & 31.59 & 50.26\tabularnewline
0.4 & 9.97 & 38.73 & 69.19 & 76.80\tabularnewline
0.5 & 21.92 & 77.20 & 84.96 & 105.84\tabularnewline
0.6 & 38.73 & 103.20 & 133.20 & 228.24\tabularnewline
0.7 & 63.94 & 138.24 & 244.80 & 871.20\tabularnewline
0.8 & 113.14 & 326.88 & 326.88 & 871.20\tabularnewline
0.9 & 166.63 & 516.00 & 871.20 & 871.20\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[c]{@{}lrrr@{}}
\caption{Confusion matrix comparing chlorophyll \textit{a} predicted
exceedences (rows) versus real exceedances (columns) for the USEPA
childrens drinking water advisory.
\label{tab:child_conmat_table}}\tabularnewline
\toprule
& Not Exceed & Exceed & Row Totals\tabularnewline
\midrule
\endfirsthead
\toprule
& Not Exceed & Exceed & Row Totals\tabularnewline
\midrule
\endhead
Not Exceed & 638 & 93 & 731\tabularnewline
Exceed & 173 & 124 & 297\tabularnewline
Column Totals & 811 & 217 & 1028\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[c]{@{}lrrr@{}}
\caption{Confusion matrix comparing chlorophyll \textit{a} predicted
exceedences (rows) versus real exceedances (columns) for the WHO
drinking water advisory.
\label{tab:who_drink_conmat_table}}\tabularnewline
\toprule
& Not Exceed & Exceed & Row Totals\tabularnewline
\midrule
\endfirsthead
\toprule
& Not Exceed & Exceed & Row Totals\tabularnewline
\midrule
\endhead
Not Exceed & 850 & 82 & 932\tabularnewline
Exceed & 57 & 39 & 96\tabularnewline
Column Totals & 907 & 121 & 1028\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[c]{@{}lrrr@{}}
\caption{Confusion matrix comparing chlorophyll \textit{a} predicted
exceedences (rows) versus real exceedances (columns) for the USEPA adult
drinking water advisory. \label{tab:adult_conmat_table}}\tabularnewline
\toprule
& Not Exceed & Exceed & Row Totals\tabularnewline
\midrule
\endfirsthead
\toprule
& Not Exceed & Exceed & Row Totals\tabularnewline
\midrule
\endhead
Not Exceed & 887 & 57 & 944\tabularnewline
Exceed & 50 & 34 & 84\tabularnewline
Column Totals & 937 & 91 & 1028\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[c]{@{}lrrr@{}}
\caption{Confusion matrix comparing chlorophyll \textit{a} predicted
exceedences (rows) versus real exceedances (columns) for the WHO
recreational water advisory.
\label{tab:who_rec_conmat_table}}\tabularnewline
\toprule
& Not Exceed & Exceed & Row Totals\tabularnewline
\midrule
\endfirsthead
\toprule
& Not Exceed & Exceed & Row Totals\tabularnewline
\midrule
\endhead
Not Exceed & 910 & 52 & 962\tabularnewline
Exceed & 43 & 23 & 66\tabularnewline
Column Totals & 953 & 75 & 1028\tabularnewline
\bottomrule
\end{longtable}

>>>>

\documentclass[10pt,a4paper,twocolumn]{article}
\usepackage{components/f1000_styles}
\usepackage{hyperref}
\usepackage{longtable}
\bibliography{components/manuscript}

@@

Cyanobacteria harmful algal blooms (cHABs) are associated with a wide
range of adverse health effects that stem mostly from the presence of
cyanotoxins. To help protect against these impacts, several health
advisory levels have been set for some toxins. In particular, one of the
more common toxins, microcystin, has several advisory levels set for
drinking water and recreational use. However, compared to other water
quality measures, field measurements of microcystin are not commonly
available due to cost and advanced understanding required to interpret
results. Addressing these issues will take time and resources. Thus,
there is utility in finding indicators of microcystin that are already
widely available, can be estimated quickly and in situ, and used as a
first defense against high levels of microcystin. Chlorophyll \emph{a}
is commonly measured, can be estimated \emph{in situ}, and has been
shown to be positively associated with microcystin. In this paper, we
use this association to provide estimates of chlorophyll a
concentrations that are indicative of a higher probability of exceeding
select health advisory concentrations for microcystin-LR. Using the 2007
National Lakes Assessment and a conditional probability approach, we
identify chlorophyll \emph{a} concentrations that are more likely than
not to be associated with an exceedance of a microcystin health advisory
level. We look at the recent US EPA health advisories for drinking water
as well as the World Health Organization levels for drinking water and
recreational use and identify a range of chlorophyll \emph{a}
thresholds. A 50\% chance of exceeding one of the specific advisory
microcystin concentrations of 0.3, 1, 1.6, and 2 g/L is associatied with
chlorophyll \emph{a} concentration thresholds of 24.64, 65.6, 89.71, and
94.93, respectively. When managing for these various microcystin levels,
exceeding these reported chlorophyll \emph{a} concentrations should be a
trigger for further testing and possible management action.

@@

@@

\begin{tabular}{l|l|l}
\hline
Source & Type & Concentration\\
\hline
USEPA & Adult Drinking Water Advisory & 1.6 \$\textbackslash{}mu\$g/L\\
\hline
USEPA & Child Drinking Water Advisory & 0.3 \$\textbackslash{}mu\$g/L\\
\hline
WHO & Drinking Water & 1 \$\textbackslash{}mu\$g/L\\
\hline
WHO & Recreational: High Prob. of Effect & 20-2000 \$\textbackslash{}mu\$g/L\\
\hline
WHO & Recreational: Low Prob. of Effect & 2-4 \$\textbackslash{}mu\$g/L\\
\hline
WHO & Recreational: Moderate Prob. of Effect & 10-20 \$\textbackslash{}mu\$g/L\\
\hline
WHO & Recreational: Very High Prob. of Effect & >2000 \$\textbackslash{}mu\$g/L\\
\hline
\end{tabular}

:Various suggested microcystin-LR health advisory concentrations.
\label{tab:microcystin_levels}

@@

\begin{tabular}{r|r|r|r|r}
\hline
Cond. Probability & USEPA Child & WHO Drink & USEPA Adult & WHO Recreational\\
\hline
0.1 & 0.07 & 0.07 & 0.07 & 1.17\\
\hline
0.2 & 0.07 & 4.48 & 10.67 & 18.24\\
\hline
0.3 & 2.78 & 17.49 & 31.59 & 50.26\\
\hline
0.4 & 9.97 & 38.73 & 69.19 & 76.80\\
\hline
0.5 & 21.92 & 77.20 & 84.96 & 105.84\\
\hline
0.6 & 38.73 & 103.20 & 133.20 & 228.24\\
\hline
0.7 & 63.94 & 138.24 & 244.80 & 871.20\\
\hline
0.8 & 113.14 & 326.88 & 326.88 & 871.20\\
\hline
0.9 & 166.63 & 516.00 & 871.20 & 871.20\\
\hline
\end{tabular}

:Chlorophyll \textit{a} concentrations that are associated with a 50\%
probability of exceeding a microcystin-LR health advisory concentration.
\label{tab:mc_chla_table}

@@

\begin{tabular}{l|r|r|r}
\hline
  & Not Exceed & Exceed & Row Totals\\
\hline
Not Exceed & 638 & 93 & 731\\
\hline
Exceed & 173 & 124 & 297\\
\hline
Column Totals & 811 & 217 & 1028\\
\hline
\end{tabular}

:Confusion matrix comparing chlorophyll \textit{a} predicted exceedences
(rows) versus real exceedances (columns) for the USEPA childrens
drinking water advisory. \label{tab:child_conmat_table}

@@

\begin{tabular}{l|r|r|r}
\hline
  & Not Exceed & Exceed & Row Totals\\
\hline
Not Exceed & 850 & 82 & 932\\
\hline
Exceed & 57 & 39 & 96\\
\hline
Column Totals & 907 & 121 & 1028\\
\hline
\end{tabular}

:Confusion matrix comparing chlorophyll \textit{a} predicted exceedences
(rows) versus real exceedances (columns) for the WHO drinking water
advisory. \label{tab:who_drink_conmat_table}

@@

\begin{tabular}{l|r|r|r}
\hline
  & Not Exceed & Exceed & Row Totals\\
\hline
Not Exceed & 887 & 57 & 944\\
\hline
Exceed & 50 & 34 & 84\\
\hline
Column Totals & 937 & 91 & 1028\\
\hline
\end{tabular}

:Confusion matrix comparing chlorophyll \textit{a} predicted exceedences
(rows) versus real exceedances (columns) for the USEPA adult drinking
water advisory. \label{tab:adult_conmat_table}

@@

\begin{tabular}{l|r|r|r}
\hline
  & Not Exceed & Exceed & Row Totals\\
\hline
Not Exceed & 910 & 52 & 962\\
\hline
Exceed & 43 & 23 & 66\\
\hline
Column Totals & 953 & 75 & 1028\\
\hline
\end{tabular}

:Confusion matrix comparing chlorophyll \textit{a} predicted exceedences
(rows) versus real exceedances (columns) for the WHO recreational water
advisory. \label{tab:who_rec_conmat_table}
